Properties of coronal Fourier power spectra and their implications for coronal seismology and coronal heating.

### 2014-03-27 tex/paper1/paper1.tex
edits to the paper, and an attempt to speed up fitting

\subsection{Coronal seismology and the effect of background assumptions}
\label{ssec:corseis}

@@

The foregoing discusses the implications of red-noise power spectra
for the detection of narrow-frequency band oscillations when looking
at single time-series.  The advantage of AIA is that there is more
than one time-series to consider.  Evidence for the presence of a wave
in the corona is much stronger if it can be shown that narrow
frequency-band oscillations occur significantly above a red-noise
background signal in several neighboring pixels.

Figure \ref{fig:compare171193} shows that time series from individual
pixels have power-law like power spectra.  This implications for the
design of automated oscillation detection algorithms.  Such an
algorithm must somehow take into account the nature of the power
spectrum.  The power-law power spectrum itself lacks an easily
definable time-scale at or below which a background trend can be
defined.  Automated detection algorithns that rely on background trend
subtraction such as \cite{2010SoPh..264..403I} must therefore look to
other reasons for to justify a time-scale.

As has been shown above, the assumption of a Gaussian-distributed
noise when red noise power-spectrum is actually present, coupled with
too low a confidence level, can lead to misleading results when
looking for oscillatory signals.  Many detection algorithms do make
this assumption, for example \cite{2004SoPh..223....1D},
\cite{2007SoPh..241..397N}, \cite{2008SoPh..248..395S} and
\cite{2010SoPh..264..403I}.  Such approaches {\it may} have yet to be
tested assuming a red-noise background power spectrum, and so their
efficacy is unknown.

All the automated detection algorithms described above attempt to find
pixels that are obviously oscillating at some frequency.  Hence, the
strength of the oscillation at that frequency, compared to some
assumption of the background, is the key quantity to measure.
Detection algorithms based on wave coherence, such as
\cite{2008SoPh..252..321M}, implement wave detection through finding
spatially contiguous regions of the corona which are coherent in a
given frequency range.  The frequency range searched is based on
previous experience.  These

>>>>

\subsection{Effect of background power spectrum assumptions on the
  detection of oscillatory power}
\label{ssec:corseis}

@@

\subsection{Implications for coronal seismology and automated
  oscillation detection algorithms}\label{sec:oscdetect}

The discussion of Section \ref{ssec:corseis} shows that red-noise
power spectra has a powerful effect on the claims of a detection of
narrow-frequency band oscillations in time-series.  When looking at
extended regions of coronal imaging data, evidence for the presence of
an oscillation in the corona is strengthened if it can be shown that
narrow frequency-band oscillations occur significantly above a
red-noise background signal in several neighboring pixels.  Coronal
seismology derives its observational evidence from such detections,
and automated detection algorithms hold out the hope of greatly
increasing the number of oscillating regions detected.

Figure \ref{fig:compare171193} shows that time series from individual
pixels have power-law like power spectra.  This has implications for
the design of automated oscillation detection algorithms.  Such an
algorithm must somehow take into account the nature of the power
spectrum.  The power-law power spectrum itself lacks an easily
definable time-scale at or below which a background trend can be
defined.  Automated detection algorithns that rely on background trend
subtraction such as \cite{2010SoPh..264..403I} must therefore look to
other reasons for to justify a time-scale.

As has been shown above, the assumption of a Gaussian-distributed
noise when red noise power-spectrum is actually present, coupled with
too low a confidence level, can lead to misleading results when
looking for oscillatory signals.  Many detection algorithms do make
this assumption, for example \cite{2004SoPh..223....1D},
\cite{2007SoPh..241..397N}, \cite{2008SoPh..248..395S} and
\cite{2010SoPh..264..403I}.  Such approaches have yet to be tested
assuming a red-noise background power spectrum, and so their efficacy
is unknown.  \cite{2004SoPh..223....1D} and \cite{2008SoPh..248..395S}
are wavelet-based approaches, and Figure \ref{fig:comparison} does
suggest that a red-noise background spectrum will make a significant
difference.

All the automated detection algorithms described above attempt to find
individual pixels that are obviously oscillating at some frequency,
using the strength of the oscillation at that frequency (compared to
some assumption of the background) as the key quantity to measure.
These pixels are then clumped together and the quality of the signal
is then assessed.  Detection algorithms based on wave coherence, such
as \cite{2008SoPh..252..321M}, implement wave detection through
finding spatially contiguous regions of the corona which are coherent
in a given frequency range.  The frequency range searched is based on
previous experience.  Oscillations that are detected propagating along
loops are often found by considering distance-time plots
\cite{demoortel2000} and looking for alternating brightening/darkening
in those plots as a indicator of a propagating wave.  This is
essentially a coherence-based approach, as the user is assessing the
likelihood that an oscillation has been detected based on the observed
signal in multiple contiguous pixels.  However, each pixel in these
plots probably has a red-noise background power spectrum, and so the
discussion of Section \ref{ssec:corseis} suggests that the
significance of any claimed oscillation is much reduced.  The effect
of a red-noise background signal on these coherence-based approaches
is not known.
